Epistemic Semantics in Guarded String Models\thanks{Thanks guys.}

### 2021-01-14 tex/pdraft.tex

\title{Epistemic Semantics in Guarded String Models\thanks{Thanks guys.}}
\renewcommand\footnotemark{}
%%\renewcommand\footnoterule{}

@@

\begin{figure}[!t]
  \vspace{1em}
  \centering
  \footnotesize
  %% \begin{tabular}[t]{lcc}
  %%   \toprule
  %%       \textsc{Item} & \textsc{Type} & \textsc{Semantics}\\ \midrule
  %%       Amy & $e$ & $\hat{R}_a$\\
  %%       Bob & $e$ & $\hat{R}_b$\\
  %%       it & $d$ & $d$ \\
  %%       heads & $d \backslash_D t$ & $\lambda x.\bullet^*h$ \\
  %%       tails & $d \backslash_D t$ & $\lambda x.\bullet^*t$ \\
  %%       is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P~x.~P~x$ \\
  %%       knows & $(e \backslash t)\slash_M t$ &  $\lambda p~R.~p\vee{\Diamond}_Rp$\\
  %%       believes & $(e \backslash t)\slash_M t$ &  $\lambda p~R.~{\Diamond}_Rp$\\
  %%       that  & $(((e \backslash t){\slash_M}t) \backslash (e \backslash t)) \slash t$
  %%       & $\lambda p\,m\,R.{\neg}(m\,({\neg}p)\,R)$ \\
  %%       whether  & $(((e \backslash t){\slash_M} t) \backslash (e \backslash t)) \slash t$
  %%       & $\lambda p\,m\,R.{\neg}(m\,({\neg}p)\,R)$ \\
  %%       && \multicolumn{1}{r}{$+ {\neg}(m\,p\,R)$} \\ \bottomrule
  %% \end{tabular}

  \newcommand{\hdrspc}{0.3em}
    \begin{tabular}[t]{l>{\hspace{-.8em}}c >{\hspace{-.6em}}c}
    \toprule
    \textsc{Item} & \textsc{Type} & \textsc{Semantics}\\ \midrule
    \multicolumn{3}{c}{{\bf Statives with expletive subject}} \\[\hdrspc]
        heads & $d \backslash_D t$ & $\lambda x.\,\bullet^*h$ \\
        tails & $d \backslash_D t$ & $\lambda x.\,\bullet^*t$ \\ \midrule
    \multicolumn{3}{c}{{\bf Agents}} \\
        Amy & $e$ & $\hat{R}_a$\\
        Bob & $e$ & $\hat{R}_b$\\ \midrule
    \multicolumn{3}{c}{{\bf Auxiliary verbs and expletive subjects}} \\[\hdrspc]
        it & $d$ & {\em{dummy}} \\
        is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P\,x.\,P\,x$ \\
        it's & $(t \slash(d \backslash_D t)$ & $\lambda P\,x.\,P\,x$ \\
        isn't & $t\slash(d \backslash_D t)$ & $\lambda P\,x.\,\neg P\,x$ \\
        doesn't & $(e \backslash t)\slash(d \backslash_V t)$ & $\lambda P\,x.\,\neg P\,x$ \\  \midrule
    \multicolumn{3}{c}{{\bf Tensed attitude verbs}} \\[\hdrspc]
        knows & $(e \backslash t)\slash_M t$ &  $\lambda p\,R.\,p + {\Diamond}_Rp$\\
        believes & $(e \backslash t)\slash_M t$ &  $\lambda p\,R.\,{\Diamond}_Rp$\\ \midrule
    \multicolumn{3}{c}{{\bf Base form attitude verbs}} \\[\hdrspc]
        know & $(e \backslash_V t)\slash_M t$ &  $\lambda p\,R.\,p + {\Diamond}_Rp$\\
        believe & $(e \backslash_V t)\slash_M t$ &  $\lambda p\,R.\,{\Diamond}_Rp$\\ \midrule
    \multicolumn{3}{c}{{\bf Complementizers}} \\[\hdrspc]
        that  & $(((e \backslash t){\slash_M}t) \backslash (e \backslash t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
          \,\,{\neg}(m\,({\neg}p)\,R)
        \end{pmatrix*}$ \\[1.1em]
        whether  & $(((e \backslash t){\slash_M} t) \backslash (e \backslash t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
                  \,\, {\neg}(m\,({\neg}p)\,R) \\
          \,\,\,\, +\,{\neg}(m\,p\,R)
        \end{pmatrix*}$\\ \midrule
    \multicolumn{3}{c}{{\bf Complementizers for base form verbs}} \\[\hdrspc]
        that  & $(((e \backslash_V t){\slash_M}t) \backslash (e \backslash_V t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R. \\
          \,\, {\neg}(m\,({\neg}p)\,R)
        \end{pmatrix*}$ \\[1.1em]
        whether & $(((e \backslash_V t){\slash_M} t) \backslash (e \backslash_V t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
                  \,\, {\neg}(m\,({\neg}p)\,R) \\
          \,\,\,\, +\,{\neg}(m\,p\,R)
        \end{pmatrix*}$ \\
        \bottomrule
      \end{tabular}%%
    \caption{Categorial grammar lexicon, showing word form (column 1), a
      categorial type (column 2), and a semantic translation in Epik extended
      with lambda abstraction (column 3).}
  \label{lexiconfigure}
\end{figure}

>>>>

\title{Epistemic Semantics in Guarded String Models\thanks{Thanks to Tobias Kappe for insightful reactions to the paper.
Thanks also to three SCiL reviewers for helpful comments.
Earlier versions of the work were presented in the LUSH talk series at Utrecht in December 2019, and in the Workshop on formal/philosophical/computational approaches to natural language meaning at Rochester in December 2020.  Thanks to the audiences for their reactions.
    .}}
\renewcommand\footnotemark{}
%%\renewcommand\footnoterule{}

@@

\newcommand{\ebackt}{(e \backslash t)}
\begin{figure}[!t]
  \vspace{1em}
  \centering
  \footnotesize
  %% \begin{tabular}[t]{lcc}
  %%   \toprule
  %%       \textsc{Item} & \textsc{Type} & \textsc{Semantics}\\ \midrule
  %%       Amy & $e$ & $\hat{R}_a$\\
  %%       Bob & $e$ & $\hat{R}_b$\\
  %%       it & $d$ & $d$ \\
  %%       heads & $d \backslash_D t$ & $\lambda x.\bullet^*h$ \\
  %%       tails & $d \backslash_D t$ & $\lambda x.\bullet^*t$ \\
  %%       is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P~x.~P~x$ \\
  %%       knows & $(e \backslash t)\slash_M t$ &  $\lambda p~R.~p\vee{\Diamond}_Rp$\\
  %%       believes & $(e \backslash t)\slash_M t$ &  $\lambda p~R.~{\Diamond}_Rp$\\
  %%       that  & $(((e \backslash t){\slash_M}t) \backslash (e \backslash t)) \slash t$
  %%       & $\lambda p\,m\,R.{\neg}(m\,({\neg}p)\,R)$ \\
  %%       whether  & $(((e \backslash t){\slash_M} t) \backslash (e \backslash t)) \slash t$
  %%       & $\lambda p\,m\,R.{\neg}(m\,({\neg}p)\,R)$ \\
  %%       && \multicolumn{1}{r}{$+ {\neg}(m\,p\,R)$} \\ \bottomrule
  %% \end{tabular}

  \newcommand{\hdrspc}{0.3em}
    \begin{tabular}[t]{l>{\hspace{-.8em}}c >{\hspace{-.6em}}c}
    \toprule
    \textsc{Item} & \textsc{Type} & \textsc{Semantics}\\ \midrule
    \multicolumn{3}{c}{{\bf Statives with expletive subject}} \\[\hdrspc]
        heads & $d \backslash_D t$ & $\lambda x.\,\bullet^*h$ \\
        tails & $d \backslash_D t$ & $\lambda x.\,\bullet^*t$ \\ \midrule
    \multicolumn{3}{c}{{\bf Agents}} \\
        Amy & $e$ & $\hat{R}_a$\\
        Bob & $e$ & $\hat{R}_b$\\ \midrule
    \multicolumn{3}{c}{{\bf Auxiliary verbs and expletive subjects}} \\[\hdrspc]
        it & $d$ & {\em{dummy}} \\
        is & $(d \backslash t)\slash(d \backslash_D t)$ & $\lambda P\,x.\,P\,x$ \\
        it's & $(t \slash(d \backslash_D t)$ & $\lambda P\,x.\,P\,x$ \\
        isn't & $t\slash(d \backslash_D t)$ & $\lambda P\,x.\,\neg P\,x$ \\
        doesn't & $(e \backslash t)\slash(d \backslash_V t)$ & $\lambda P\,x.\,\neg P\,x$ \\  \midrule
    \multicolumn{3}{c}{{\bf Tensed attitude verbs}} \\[\hdrspc]
        knows & $(e \backslash t)\slash_M t$ &  $\lambda p\,R.\,p + {\Diamond}_Rp$\\
        believes & $(e \backslash t)\slash_M t$ &  $\lambda p\,R.\,{\Diamond}_Rp$\\ \midrule
    \multicolumn{3}{c}{{\bf Base form attitude verbs}} \\[\hdrspc]
        know & $(e \backslash_V t)\slash_M t$ &  $\lambda p\,R.\,p + {\Diamond}_Rp$\\
        believe & $(e \backslash_V t)\slash_M t$ &  $\lambda p\,R.\,{\Diamond}_Rp$\\ \midrule
    \multicolumn{3}{c}{{\bf Complementizers}} \\[\hdrspc]
        that  & $(((e \backslash t){\slash_M}t) \backslash (e \backslash t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
          \,\,{\neg}(m\,({\neg}p)\,R)
        \end{pmatrix*}$ \\[1.1em]
        whether  & $(((e \backslash t){\slash_M} t) \backslash (e \backslash t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
                  \,\, {\neg}(m\,({\neg}p)\,R) \\
          \,\,\,\, +\,{\neg}(m\,p\,R)
        \end{pmatrix*}$\\ \midrule
    \multicolumn{3}{c}{{\bf Complementizers for base form verbs}} \\[\hdrspc]
        that  & $(((e \backslash_V t){\slash_M}t) \backslash (e \backslash_V t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R. \\
          \,\, {\neg}(m\,({\neg}p)\,R)
        \end{pmatrix*}$ \\[1.1em]
        whether & $(((e \backslash_V t){\slash_M} t) \backslash (e \backslash_V t)) \slash t$
        & $\begin{pmatrix*}[l]
          \lambda p\,m\,R.\\
                  \,\, {\neg}(m\,({\neg}p)\,R) \\
          \,\,\,\, +\,{\neg}(m\,p\,R)
        \end{pmatrix*}$ \\ \midrule
        \multicolumn{3}{c}{{\bf Conjunction}} \\[\hdrspc]
        and & $(t \backslash t)\slash t$ &  $\lambda p\,q.\,p \wedge q$\\
        or & $(t \backslash t)\slash t$ &  $\lambda p\,q.\,p + q$\\
        and & $((\ebackt \backslash \ebackt)\slash \ebackt$ &  $\lambda p\,q\,x.\,p(x) \wedge q(x)$\\
        or & $((\ebackt \backslash \ebackt)\slash \ebackt$ &  $\lambda p\,q\,x.\,p(x) + q(x)$\\        
        \bottomrule
      \end{tabular}%%
    \caption{Categorial grammar lexicon, showing word form (column 1), a
      categorial type (column 2), and a semantic translation in Epik extended
      with lambda abstraction (column 3).}
  \label{lexiconfigure}
\end{figure}
